A distance metric between histograms through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-10-31 tables/musicGeneral_.tex
terminada polida nas tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c |}\hline
label & description & events \\\hline
Pale & Sanctus 69 from G. P. da Palestrina  & 719.00 \\\hline
Bach1 & BWV735 from J. S. Bach  & 236.00 \\\hline
Bach2 & BWV648 from J. S. Bach  & 272.00 \\\hline
Moza1 & K80 from W. A. Mozart  & 538.00 \\\hline
Moza2 & K458 from W. A. Mozart  & 4218.00 \\\hline
Beet1 & Opus 18, n1, mov. 3 from L. van Beethoven  & 1289.00 \\\hline
Beet2 & Opus 132 from L. van Beethoven  & 17884.00 \\\hline
Sch\"on & Opus 19, mov. 2 from A. Sch\"onberg  & 102.00 \\\hline
\end{tabular}
\caption{General description of the music data used for the $c$ values of the next table. Each event is a midi value of a note pitch. Samples where chosen to reflect music history timeline. Works by the same composer were chosen among the first and last 10\% of all he produced.}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || c | c |}\hline
label & description & events \\\hline\hline
{\bf Pale} & Sanctus 69 from G. P. da Palestrina & 719.00 \\\hline
{\bf Bach1} & BWV735 from J. S. Bach & 236.00 \\\hline
{\bf Bach2} & BWV648 from J. S. Bach & 272.00 \\\hline
{\bf Moza1} & K80 from W. A. Mozart & 538.00 \\\hline
{\bf Moza2} & K458 from W. A. Mozart & 4218.00 \\\hline
{\bf Beet1} & Opus 18, n1, mov. 3 from L. van Beethoven & 1289.00 \\\hline
{\bf Beet2} & Opus 132 from L. van Beethoven & 17884.00 \\\hline
{\bf Sch\"on} & Opus 19, mov. 2 from A. Sch\"onberg & 102.00 \\\hline
\end{tabular}
\caption{General description of the music data used for the $c$ values of the next table. Each event is a midi value of a note pitch. Samples where chosen to reflect music history timeline. Works by the same composer were chosen among the first and last 10\% of all he produced.}
\end{center}
\end{table}
